### 2016-09-12 plosOneJordanousKeller/PAPER/S1_appendix.tex
changes to image and appendices

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
%\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use strikethrough for track changes 
\usepackage[normalem]{ulem}
% command is \sout{text text text etc}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Modelling Creativity: Identifying Key Components through a Corpus-Based Approach}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Anna Jordanous\textsuperscript{1,\Yinyang, *},
Bill Keller\textsuperscript{2,\Yinyang}
\\
\bigskip
\bf{1} School of Computing, University of Kent, Chatham Maritime, Kent, UK
\\
\bf{2} Department of Informatics, University of Sussex, Falmer, Brighton, UK
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* a.k.jordanous@kent.ac.uk / billk@sussex.ac.uk

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}

Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours. If we wish to study creativity scientifically, then a tractable and well-articulated model of creativity is required. Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice. This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people use to describe the concept. Using techniques from the field of statistical natural language processing, we identify a collection of fourteen key components of creativity through an analysis of a corpus of academic papers on the topic. Words are identified which appear significantly often in connection with discussions of the concept. Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerge, which collectively contribute to a comprehensive and multi-perspective model of creativity. The components provide an ontology of creativity: a set of building blocks which can be used to model creative practice in a variety of domains. The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating achievements of this work and directions for further research.

\linenumbers

\section*{Introduction}\label{intro}

%Currently, most content on the Semantic Web is in the form of ontologies of `things': semantically structured collections of factual or objective data on topics as diverse as people \cite{foaf}, places \cite{geonames}, music \cite{musicOntology} or manuscripts \cite{sawsOntology}. The focus in Semantic Web research has generally been on reducing ambiguity in representations of these more structured domains and concepts, rather than directly tackling the representation and machine-readable representation of subjective, unstructured concepts in an ontology. However, cognitive science research and work on lexical resources such as WordNet \cite[$http://wordnet.rkbexplorer.com$]{fellbaum98} have laid foundations for more definitionally troublesome concepts to be considered in detail. The time is ripe for developing ontologies of subjective concepts such as creativity.

What is creativity, and how can we better understand and learn about creativity using computational modelling? Computational creativity is a relatively youthful research area that has been growing with significant pace in recent years. Computational creativity is: 
\begin{quote}`The philosophy, science and engineering of computational systems which, by taking on particular responsibilities, exhibit behaviours that unbiased observers would deem to be creative.' 
\cite{coltonwiggins12} (p. 21).
\end{quote}

Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences, and engineering. Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling (for examples, see \cite{colton08,widmerAIM09,leon10MM,perezyperez99}).

The evaluation of creative systems developed by researchers in the field of computational creativity has proven non-trivial. Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}. Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about `creativity' and what does it constitute?

Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours. There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in \nameref{S1_Appendix}). 
In the academic literature on creativity, many common themes have emerged. 
However, multiple viewpoints exist, prioritising different aspects of the concept according to what are traditionally considered to be the primary factors for a particular discipline. 
The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}. Such a meta-level account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.

There are many challenges to modelling a concept like creativity in a computational setting. Conceptually, creativity seems inherently fuzzy or vague, with a meaning that shifts depending on the domain of application. Tackling these challenges affords two key advantages, both of which motivate the current paper. First, we can take advantage of computing and artificial intelligence to perform or enhance creative activities using computational power and research expertise. Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.

The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints. We present a novel, empirical approach to the problem of modelling how creative behaviour is manifested, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept. Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}. The current work is intended as a significant, methodological contribution towards addressing the Grand Challenge of evaluation in computational creativity research. It should provide researchers with a firm foundation for evaluating exactly how creative so-called {\emph creative systems} actually are.

On our approach, statistical language processing techniques are used to identify words significantly associated with creativity in a corpus of academic papers on the subject. A corpus spanning some 60 years of research into the nature of creativity was collected together. The papers were gathered from a wide variety of disciplines including psychology, educational testing and computational creativity, amongst others. The language data drawn from this collection was then analysed and contrasted with data from a corpus of matched papers on subjects unrelated to creativity. From this analysis, a set of 694 {\em creativity words\/} was identified, where each creativity word appeared significantly more often than expected in the corpus of creativity papers. A measure of lexical similarity provided a basis for clustering the creativity words into groups of words with similar or shared aspects of meaning. Through inspection of these clusters, a total of fourteen {\em key components of creativity\/} was identified, where each represents a key theme or attribute of creativity. The set of components yields information about the nature of creativity, based on what is collectively emphasised in discussions about the concept.

% The Semantic Web has emerged as a way to address the troublesome but important issue \cite{boden99} of articulating values, concepts and information using an open and  {\em machine-understandable} vocabulary. Encoding the creativity components in an OWL ontology has enabled this {\em ontology of creativity} to be made publicly available to the wider research community as a resource in the Semantic Web, under the permanent URL:
%\begin{quote}
%{\small \texttt{http://purl.org/creativity/ontology}}
%\end{quote}

In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is considered.
%, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
In the remaining sections, details are provided of the methodology used to identify components of creativity from an analysis of language data. The results of this analysis are then presented in terms of a model that encompasses fourteen key components. The derived set of components is evaluated in terms of how well it satisfies the need for a shared, inclusive and comprehensive account of creativity and provides a vocabulary of creativity that is accessible to both people and machines. Finally, conclusions are drawn and some directions for further work are outlined.

\subsection*{Background:  The nature of creativity} \label{background}

As Torrance observes:

\begin{quote}
`[c]reativity defies precise definition ... even if we had a precise conception of creativity, I am certain we would have difficulty putting it into words' \cite{torrance88} (p.43). 
\end{quote}

Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
In their review of research into human creativity, Hennessey and Amabile ask a significant follow-on question: 
\begin{quote}
`Even if this mysterious phenomenon can be isolated, quantified, and dissected, why bother? Wouldn't it make more sense to revel in the mystery and wonder of it all?' 
\cite{hennessey10} (p.570).
\end{quote}

\noindent Two answers to this question are offered by Hennessey and Amabile, both of which are identified as desirable: to gain a deeper understanding of creativity and to learn how to boost people's creativity.

Creativity can and should be studied and measured scientifically, but the lack of a commonly-agreed understanding causes problems for measurement \cite{kaufman09}. Plucker et al. make recommendations about best practice based on their own survey of the creativity literature:
\begin{quote}
\noindent
`we argue that creativity researchers must

\begin{enumerate}
\renewcommand{\labelenumi}{(\alph{enumi})}
\item explicitly define what they mean by creativity,
\item avoid using scores of creativity measures as the sole definition of creativity (e.g., creativity is what creativity tests measure and creativity tests measure creativity, therefore we will use a score on a creativity test as our outcome variable),
\item discuss how the definition they are using is similar to or different from other definitions, and
\item address the question of creativity for whom and in what context.' \cite{plucker04defn} (p.92).
\end{enumerate}
\end{quote}

\noindent In short, we need to specify and justify the standards that we use to judge creativity. A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}. Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite{vartanian14} (p.15), based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.

\paragraph{Definitions of creativity.}
\label{existing_defs}

To find out the meaning of a word, a natural first step might be to consult a dictionary. Dictionary definitions of creativity provide a brief introduction to  the meaning of the word. However, for the purposes of research, the utility of such definitions is severely restricted by their format and brevity, and they generally provide only cursory, shallow insights into the nature of creativity. More problematic still, dictionary entries are often self-referential or circular,  defining creativity in terms of ``being creative'' or ``creative ability''. To illustrate these limitations, there follow several typical dictionary definitions of creativity and the related words `creative' and `create'. For readability, some definitions are edited slightly to standardise formats and remove etymological/grammatical annotations:
\begin{quotation}
\begin{description}
\item {\em Oxford English Dictionary} 2nd ed. (1989) pp. 1134-5:
	\begin{enumerate}
	\item[creativity:] creative power or faculty; ability to create
	\item [creative:] Having the quality of creating, able to create; of or relating to creation; originative. b. Inventive, imaginative; of, relating to, displaying, using, or involving imagination or original ideas as well as routine skill or intellect, esp. in literature or art. c. Esp. of a financial or other strategy: ingenious, esp. in a misleading way. 2. Providing the cause or occasion of, productive of.
\item [create:] 1.a. Said of the divine agent: To bring into being, cause to exist; esp. to produce where nothing was before, 'to form out of nothing'. b. with complemental extension. 2. To make, form, constitute, or bring into legal existence (an institution, condition, action, mental product, or form, not existing before). Sometimes of material works. 3. To constitute (a personage of rank or dignity); to invest with rank, title, etc. 4. To cause, occasion, produce, give rise to (a condition or set of circumstances).
	\end{enumerate}
\item {\em The Penguin English Dictionary} 2nd ed. (1969) p. 174:
	\begin{enumerate}
	\item[creativity:] creative power or faculty; ability to create
	\item[creative:] having power to create; related to process of creation; constructive, original, producing an essentially new product; produced by original intellectual or artistic effort 
	\item [create:] make out of nothing, bestow existence on; cause, bring about; produce or make something new or original; confer new rank etc on; (theat) be the first to act (a certain part); make a fuss
	\end{enumerate}
\item {\em Webster's 3rd New International Dictionary} (1961) p. 532:
	\begin{enumerate}
	\item[creativity:] the quality of being creative; ability to create 
	\item[creative:] 1. having the power or quality of creating; given to creation 2: PRODUCTIVE - used with 3: having the quality of something created rather than imitated or assembled; expressive of the maker; IMAGINATIVE 
	\item[create:] 1: to bring into existence; make out of nothing and for the first time 2: to cause to be or to produce by fiat or by mental, moral, or legal action 3: to cause or occasion - used of natural or physical causes and esp. of social and evolutionary or emergent forces 4a: to produce (as a work of art or of dramatic interpretation) along new or unconventional lines) b: to design (as a costume or dress)
	\end{enumerate}
\end{description}
\end{quotation}

Given the problems inherent in dictionary definitions of creativity, it is not surprising that a number of creativity researchers have set out  to provide their own definitions of the concept.  Some examples are:

\begin{quotation}
\begin{quote}
 `creativity is that process which results in a novel work that is accepted as tenable or useful or satisfying by a group at some point in time' %By this definition we limit ourselves to the study of individuals who are regarded as creative by ``significant others'' in their environment.'
\cite{stein63} (p.28)
\end{quote}
%\begin{quote}
%`A product or response will be judged as creative to the extent that (a) it is both a novel and appropriate, useful, correct or valuable response to the task at hand, and (b) the task is heuristic rather than algorithmic.'
%\cite[p. 35]{amabile96}
%\end{quote}
\begin{quote}
`Creativity is the ability to produce work that is both novel (i.e., original, unexpected) and appropriate (i.e., useful, adaptive concerning task constraints)'
\cite{sternberg99a}(p.3)
\end{quote}
\begin{quote}
`Creativity is the ability to come up with ideas or artefacts that are {\em new}, {\em surprising and valuable}'
\cite{boden04}(p.1)
\end{quote}
\begin{quote}
`Creativity is the interaction among \emph{aptitude, process, and environment} by which an individual or group produces a \emph{perceptible product} that is both \emph{novel and useful} as defined within a \emph{social context}'
\cite{plucker04defn}(p.90)
\end{quote}
\begin{quote}
`Creativity: the generation of products or ideas that are both novel and appropriate' 
\cite{hennessey10}(p.570)
\end{quote}
\begin{quote}
`The word creativity is a noun naming the phenomenon in which a person communicates a new concept (which is the product). Mental activity (or mental process) is implicit in this definition, and of course no one could conceive of a person living or operating in a vacuum, so the term \emph{press} is also implicit'
\cite{rhodes61}(p.305)
\end{quote}
\end{quotation}

These more research-oriented definitions avoid the problems of self-reference and circularity noted for the dictionary entries given previously. However, whilst the definitions may provide somewhat deeper insight into the nature of creativity, the brevity of the definitions means that they still only succeed in providing shallow, summary accounts of the concept.

\paragraph{A multitude of different perspectives} \label{perspectives}

The problem of identifying and quantifying creativity exists across many disciplines. How creative is this person? Does this person have the creative abilities to boost my business? Is this pupil's story creative? Is this computational system an example of computational creativity? As a consequence, when attempts are made to define creativity, it is often from the perspective of a particular domain or research discipline. For example, psychometric tests for creativity such as \cite{guilford50,torrance74} focus on {\em problem solving} and {\em divergent thinking} as key attributes of a creative person. In contrast, computational creativity research (for examples see \cite{pease01,wiggins06ngc,peinado06ngc,ritchie07}) has historially placed emphasis on the {\em novelty} and {\em value} of creative products. Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity. These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.

Several competing interpretations of creativity exist in the literature. Sometimes these differences of opinion do not need to be directly resolved but can be included alongside each other. Examples include whether creativity is centred around mental processes \cite{boden04,dietrich10,gabora12} or embodied and situated in an interactive environment \cite{mccormack07,sosa09}. Another example is whether creativity is domain-independent \cite{plucker98}, or dependent on domain-specific context \cite{baer98}, or (as both Plucker and Baer have concluded) a combination of both \cite{plucker04,baer10}.

Other conflicts arise where a previously narrow view of creativity has been widened in perspective. To resolve the conflict, an inclusive, all-encompassing view of creativity should adopt the wider perspective and incorporate the narrower perspective. For example rather than focussing narrowly on creative {\em genius}, through the study of people with exceptional creative achievements (see \cite{poincare29,hadamard45}) emphasis has shifted to encompass the broader study of {\em everyday} creativity, with genius as a special case: the notion that everyone can be creative to some degree \cite{weisberg88,bryankinns09}.

Similarly, researchers distinguish between {\em little-c} and {\em Big-C} creativity, or {\em psychological/P-creativity} and  {\em historical/H-creativity} \cite{boden04}, adjusting their focus accordingly to make their research more manageable. This is particularly the case in computational creativity, where endowing the computer with elements of general, human knowledge and experience is a major challenge. Little-c creative or p-creative work is perceived as creative by the creator personally but may replicate existing work (unknown to the creator) so is not necessarily creative in a wider social context. This encompasses the concept of Big-C creativity or h-creativity, where the work makes a creative contribution both to the creator and to society. To be Big-C creative/h-creative is to be little-c creative/p-creative in a way which has not been done before by anyone.

The preceeding discussion indicates that creativity is a complex, multi-faceted concept that requires a broad and inclusive treatment. The {\em Four Ps} framework \cite{rhodes61,stein63,mooney63,odena09,jordanous16cs} ensures we pay attention to four key aspects of creativity:

\begin{description}
\setlength{\labelwidth}{1.5cm}
\setlength{\itemindent}{1.5cm}
\item[Person/Producer:] The individual that is creative
\item[Process:] What the creative individual does to be creative
\item[Product:] What is produced as a result of the creative process
\item[Press:] The environment in which creative activity takes place
\end{description}

\noindent This framework presents creativity in a broader context, making our understanding of the concept more generally applicable and less specific to a domain or academic discipline. In contrast, models of the creative process \cite{wallas26,poincare29,hadamard45}, tests of people's creativity \cite{goldman64,guilford67,torrance74} or tests based on creative artefact generation \cite{amabile96,ritchie07} are useful only within a limited sphere. Jordanous \cite{jordanous16cs} has contextualised the Four Ps in a computational context, referring to the creative Producer (person or computational agent) carrying out Processes within the environmental context of a Press, to create computational Products.

\subsection*{The challenges of modelling creativity} \label{cogPhil}

% Was Reflections on the semantics of subjective concepts. Merge this together and make it more relevant to modelling creativity (specifically) rather than the general treatment it is now.

Creativity can be seen as an essentially contested concept \cite{gallie56}: it is subjective, abstract and can be interpreted in a variety of acceptable ways, such that a fixed `proper general use' is elusive \cite{gallie56} (p.167). Gallie \cite{gallie56} defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference. Although there may be consensus on the meaning of such concepts in very general terms, they may defy precise interpretation. There is not a single agreed instantiation, but instead many reasonable possibilities, influenced by changing circumstances and contexts. It is more productive to acknowledge that these different interpretations exist and refer to `the respective contributions of its various parts or features' \cite{gallie56} (p.172), rather than to argue for a single interpretation. Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances). This is what Wittgenstein refers to as `family resemblances' \cite{wittgenstein58}:

\begin{quote}
[On discussing the example of what a `game' is] `we see a complicated network of similarities overlapping and criss-crossing: sometimes overall similarities, sometimes similarities of detail. ... I can think of no better expression to characterize these similarities than ``family resemblances''; for the various resemblances between members of a family: build, features, colour of eyes, gait, temperament, etc. etc. overlap and criss-cross in the same way. And I shall say: ``games'' form a family.'
\cite{wittgenstein58} (Part 1, Paragraphs 66-67).
\end{quote}

Similarly, with creativity, different manifestations of creativity are not all necessarily required to share the same common, core elements in order to be identified as part of the creativity `family'. Rather, relationships between different manifestations reveal various shared characteristics that emerge in a similar way to Wittgenstein's `family resemblances' in language. We need to identify what those family resemblances are in the case of creativity. To understand creativity, we can investigate what resemblances exist across different instantiations of the concept.

Wittgenstein \cite{wittgenstein58} has argued that `a clear view of the aim and functioning of the words' helps us `dispers[e] the fog' that obscures a clear vision of the `working of language' \cite{wittgenstein58} (Part 1, Paragraph 5). To understand the use of a word, one must have background information and context. Wittgenstein gives the example of a chess piece, which is introduced to someone as a `king' (Paragraph 31): to understand this usage the person must already know the rules of chess, or must at least know what it means to have a piece in a game. To Wittgenstein, the semantics of words and statements are determined by how we use them, grounded in rules set by our habitual use of a word and our shared consensual practices, rather than being fixed by static, pre-assigned meanings.

%Waismann, a contemporary of Wittgenstein, has reflected on the impact of `open texture' on language, where certain words or phrases simply cannot be completely defined for all possible scenarios:

%\begin{quote}
%`Every description stretches, as it were, into a horizon of open possibilities: however far I go, I shall always carry this horizon with me.'
%\cite[p. 122]{waismann68}
%\end{quote}
Linguistics research advocates that the meaning of a word is dependent on the context it is used in \cite{firth57}. In particular, Lakoff has argued that the study of language helps reveal how people think \cite{lakoff87,lakoff80}. Words used frequently in discussions of the nature of a concept provide the context for the commonly understood meaning of that concept, as has been shown in various corpus linguistics contributions \cite{oakes98,rayson00,kilgarriff01,kilgarriff06}.

%We acknowledge that semantic ambiguity is unlikely to be resolved to a single agreed definition. Meanings can be dynamic, evolving over time and contextually dependent, rather than being fixed, with a static and unchanging prescribed definition. 
The key principle emerging across these present discussions is that the meaning of words like creativity can be modelled by identifying different aspects that collectively contribute to the meaning of the concept of creativity.

%\subsection*{Subjectivity and ambiguity on the semantic web} \label{SWsubjectivity}

%Ambiguity in semantic interpretation of terms is not an area that Semantic Web research shies away from. Ontologies are widely used to pinpoint and define what {\em things} mean in a machine-readable way, for greater clarity and precision in using various vocabularies and identifiers. Such research does not concentrate merely on those areas of interest which are simple to define and objectively clear to interpret; for example SKOS \cite{skos} provides vocabulary to organise and taxonomise knowledge, whether explicit or tacit, while FRBR-oo \cite{doerr07} defines various terms to do with bibliographical records and the works and ideas expressed within them, on various conceptual levels beyond merely the physical instantiation of a book or other written document. Upper ontologies such as Dolce \cite{gangemi02}, SUMO \cite{niles01} and Cyc \cite{reed02} have guided the objective, disambiguated expression of higher-level, cross-domain, general concepts and abstract knowledge.% An upper ontology defines higher-level vocabularies and concepts necessary to implement ontologies themselves, providing the meta-vocabulary to link specific ontologies to more general concepts.

%What is not often tackled within Semantic Web research are the types of topic discussed above, where ambiguity is unlikely to be resolved to a single agreed definition and meanings are dynamic, changing over time and contextual interpretations, rather than being fixed to a static and unchanging prescribed definition. To date, there is a lack of suitable methodologies applied in Semantic Web research to enable or assist the building of ontological representations of such topics. Existing ontology construction methodologies tend to concentrate on how to extract and represent data objectively rather than retain subjectivity in the data \cite{fernandez97,noy01,haase08}; the focus is on how best to construct ontologies in an appropriate manner rather than how to tackle {\em moving-target} issues of dynamic, perhaps unresolvable, semantics.

%There is of course much work still to be done in representing semantics on the Semantic Web; much information with fixed semantics is still to be represented in a machine readable form. With the growth of the Semantic Web, this ongoing collation and representation of knowledge is work-in-progress. As discussed above, advances in other research disciplines can assist progress in areas where there is less agreement generally over semantics. The representation of these areas and concepts on the Semantic Web is troublesome, particularly in a framework which is geared towards resolving semantic ambiguity to static, pre-assigned meanings. More established disciplines in cognitive science and related areas of research would not claim to have solved all such issues and challenges; however Semantic Web researchers can learn from advances that have been made in these disciplines. An approach informed by cross-disciplinary contributions helps Semantic Web research progress towards a broader and more complex coverage of data and their semantics.

The need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed. There is a large quantity of material contributory to a satisfactory model of creativity and a number of key contributions have been discussed during this section. What must be done now is to marshal this assortment of material and to unify different perspectives where possible, in order to avoid the disciplinary `blinkers' or compartmentalisation that is often seen in creativity research \cite{hennessey10}. In approaching the semantic representation of subjective and multi-faceted concepts, some useful guidance is offered through philosophical reflections on the meaning of such concepts.

%Further, cognitive science methodologies, {\bf IS THIS NEXT BIT TO GO?} as well as approaches to ontology learning from texts \cite{gomezperez04} {\bf END} can be harnessed to enable the representation of more semantically ambiguous concepts such as creativity

%To date, however, the Semantic Web research community has largely focused on the representation of objective concepts and resources that are relatively clearly defined.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}
\label{methodology}

Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept. In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}. This works on the principle that creativity results from several components converging and goes on to examine what these components are. Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted. This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.

Tools from natural language processing and statistical analysis are used to identify words that appear to be highly associated with dimensions of creativity, as represented in a sample of academic papers on the topic. A key innovation is the use of a statistical measure of lexical similarity, which allows the words to be clustered into coherent and semantically-related groups. Clustering reveals a number of common themes or factors of creativity, allowing the identification of a set of fourteen components that serve as building blocks for creativity.

\subsection*{Corpus data}\label{corpusData}

A sample of academic papers discussing the nature of creativity was assembled as a {\em creativity corpus\/} in 2010. This creativity corpus consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.

\vspace{0.25cm}
\begin{center}
\fbox{
\begin{minipage}{0.8\linewidth}
\textbf{Creativity corpus}: \\ a collection of thirty academic papers which explicitly discuss the nature of creativity.
\end{minipage}
}
\end{center}
\vspace{0.25cm}

The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. The strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}.

\begin{figure}[!b]
\caption{{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus.}}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/Fig1}
\label{searchCC}
\end{figure}

The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers. This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search. For example, a Computer Science conference paper on cognitive models of creativity has been included, as in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field. The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.

Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines. The inclusion criteria are as follows, listed in descending order of precedence: 
\begin{itemize}
\item Papers must have, as their primary focus, discussion of the nature of creativity.
\item Papers should be considered particularly influential. Influence was generally measured objectively, in terms of the number of times a paper had been cited by other academic authors. However, for papers published in recent years and which had consequently had little time to accrue citations, selection was based instead on a subjective judgement of influence grounded in a knowledge of the field.
\item Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009. [The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J. P. Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof). His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}. 
\item Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of creativity. Fig. \ref{disciplinaryDistribution} illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers. This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered. We should acknowledge here though that while many disciplines include creative practice, often the focus is on application rather than in depth discussion of what creativity entails. Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.
\end{itemize}

\begin{figure}[!b]
% REMOVE IMAGES FROM SUBMITTED VERSION
%%\includegraphics[scale=0.5]{images/Fig2}
\caption{{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.} \\Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}. Note that Scopus may classify a journal under more than one discipline.}
\label{disciplinaryDistribution}
\end{figure}

>>>>

\documentclass[10pt,letterpaper]{article}
\begin{document}
% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.

\section*{S1 Appendix}\label{S1_Appendix}
{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
